```{r input, include=FALSE, echo=FALSE}
## AUTHOR: Joel Ås
args <- commandArgs(TRUE)
print(args)
title <- args[2]
plots <- args[-(1:2)]

get_names <- function(png_path){
  name <- tail(strsplit(png_path, "/")[[1]], 1) %>% 
    {sub(".png","", .)}
  return(name)
}


library(rmdformats)
library(tidyverse)
library(kableExtra)
```

---
title: "`r title`"
author: "Joel Ås"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output_format:
    html_document:
        toc: True
        theme: "readthedown"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Method and data
The input data is: `r title`, this is the exemple data from the [plink tutorial](http://zzz.bwh.harvard.edu/plink/tutorial.shtml). Each variant ID is queried in ensabmbl's variant database to find associated genes IDs through the R library `BioMart`. Each unique gene KEGG BRITE hierarchy is queried using R-library `KEGGREST`. The BRITE annotation data is transfromed into a feature matrix (`r paste0(title, ".mat")`) and gene annotation data is saved under (`r paste0(title, ".ann")`).

The only association keept are those with $p \neq \O$, have a associated gene and BRITE annotation. Features with less than $5 %$ prevelance within the are also filtered out.

For each BRITE, q-values are calculated and plotted under `run_folder/plots/{association}/{brite_group}.png`.


```{r, results='asis'}
for (current_plot in plots){ 
   cat("## Group: ", get_names(current_plot), "\n") 
   cat("![]", "(../", current_plot, ")", sep="")
   cat("\n")
}
```
